Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-20 paper.tex
added toc image

\subsection{Inhomogeneity in HDFG}
An often unavoidable consequence in electronic spectroscopy is broadened lineshapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.\cite{Carlson1990line, Dong2015}
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,\tilde{v}'}$ is $\omega_{e\tilde{v}'} + c\xi$, where c is a shift coefficient.
When two modes are positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
For simplicity, we assume c = $\pm$1.

We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Desiderio1979, Dick83_1, Carlson1990line} 
\begin{equation}\label{contour}
	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)}
\end{equation} 
where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
The limit of static inhomogeneity is chosen for simplicity.
While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions. \cite{Desiderio1979, Dick83_1, Carlson1990line, RN410}

Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details} 
\begin{subequations}\label{linenarrow}
	\begin{equation}\label{linenarrowa}
		\gamma_{ijkl} = \frac{- \eta_{ijkl}}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba} + \Delta_{ga}} \right)
	\end{equation}
	\begin{equation}
		\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
	\end{equation}
\end{subequations}
for correlated ($c = 1$) and anti-correlated ($c = -1$) modes, respectively.
The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
As such, the HDFG pathway considered in this work line-narrows correlated modes. 
These results are consistent with the idea that non-parametric, non-linear spectroscopies line-narrow correlated modes. \cite{Dick83_1, Carlson1990line}

@@

>>>>

\subsection{Inhomogeneity in HDFG}

An often unavoidable consequence in electronic spectroscopy is broadened line shapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
In the discussion that follows, we assume that a ground state vibrational frequency, $\ket{g,v}$, experiences variations that are correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,\tilde{v}'}$ is $\omega_{e\tilde{v}'} + c\xi$, where c is a shift coefficient.
We assume the fluctuations controlling the frequency variations are slow (the static limit), so that homogeneous lineshapes are unaffected by this fluctuation. 
When both states positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
For simplicity, we consider only c = $\pm$1.

We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Desiderio1979, Dick83_1, Carlson1990line} 
\begin{equation}\label{contour}
	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi \ P(\xi) \gamma_{ijkl}(\xi)
	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)}
\end{equation} 
where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions. \cite{Desiderio1979, Dick83_1, Carlson1990line, RN410}

Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details}

\begin{equation}\label{linenarrowa}
	\gamma_{ijkl} = \frac{- \eta_{ijkl}}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba} + \Delta_{ga}} \right)
\end{equation}
	for correlated ($c = 1$) states and
\begin{equation}
	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
\end{equation}
for anti-correlated ($c = -1$) states.
The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
As such, the HDFG pathway considered in this work line-narrows correlated modes. 
These results are consistent with the idea that non-parametric, non-linear spectroscopies line-narrow correlated modes. \cite{Dick83_1, Carlson1990line}

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{toc.png}
	\caption{
		TOC Image.
	} 
	\label{fig:toc}
\end{figure*}
